Structure Learning for $\VAR(p)$ Models

### 2019-06-17 paper/paper.tex
Simulations and nicer figures.
Comparison simulations for LASSO and PWGC.

A second and wildly successful heuristic is the LASSO regularizer
\cite{tibshirani1996regression}, which can be understood as a natural
convex relaxation to penalizing the count of the non-zero edges.  The
LASSO enjoys strong theoretical guarantees \cite{wainwright2009sharp},
even in the case of time series data \cite{basu2015}
\cite{wong2016lasso}.

The contributions of this paper are as follows: firstly, in section
\ref{sec:theory} we study \textit{pairwise} Granger-causality
relations, providing novel theorems connecting the structure of the
causality graph to the pairwise ``causality flow'' in the system, as
well as a characterization of the sparsity pattern of matrices arising
in the Wold decomposition.  We establish sufficient conditions
(sections \ref{sec:strongly_causal_graphs},
\ref{sec:persistent_systems}) under which a fully conditional
Granger-causality graph can be recovered from pairwise tests alone
(section \ref{sec:pairwise_algorithm}).  Secondly, we propose in
section \ref{sec:structure_learning} alternative graph search
heuristics inspired by our theoretical results.  Our heuristics are
compared against a standard grouped LASSO algorithm
\cite{yuan2006model} as well as local search hill climbing (\hl{state
  here the results}).  In section \ref{sec:application} we develop an
example application (\hl{more detail...}).  And provide concluding
remarks on further open problems in our conclusion (section
\ref{sec:conclusion}).

%% -Can we also formulate an SDP relaxation?
%% -Fit trees jointly or via coordinate descent?

@@

  \begin{enumerate}
    \item{$\mathcal{A} \perp \mathcal{B}\ |\ \mathcal{X}$}
    \item{$\linE{\beta}{\mathcal{A} \vee \mathcal{X}} = \linE{\beta}{\mathcal{X}}\ \forall \beta \in \mathcal{B}.$}
    % \item{$\linE{\beta}{\mathcal{A}} = \linE{\linE{\beta}{\mathcal{X}}}{\mathcal{A}}\ \forall \beta \in \mathcal{B}}$}
    \end{enumerate}

@@

\subsection{Model Order Selection}
\label{sec:model_order_selection}
There are a variety of methods to choose the filter orders $p_i$ and
$p_j$ \hl{TODO: cite some more}, we will focus in particular on the
Bayesian Information Criteria (BIC).  The BIC is substantially more
conservative than the Akaiake Information Criteria, and since we are
searching for \textit{sparse graphs}, we therefore prefer the BIC. For
the bivariate case we focus for simplicity on $p_i = p_j$ and write
simply\footnote{We use the same $p$ for the bivariate case, but this
  need not be the same as the corresponding univariate estimate}
$x_{ij}^{(p)}$, in which case the BIC, which we seek to
\textit{maximize} over $p$ is given by:

\begin{equation}
  \label{eqn:bic}
  \begin{aligned}
    BIC_{\text{univariate}}(p) &= -(T - p - 1) \ln \xi_i(p) - p\ln T,\\
    BIC_{\text{bivariate}}(p) &= -(T - p - 1) \ln \xi_{ij}(p) - 2p\ln T.\\
  \end{aligned}
\end{equation}

@@

\section{Structure Learning}
\label{sec:structure_learning}
\subsection{Local Search Heuristics}

\subsection{Edge-Wise Grouped LASSO}
Minimize the sparsity promoting regularized least squares problem and choose the hyper-parameters against the Akaike information criteria.

\begin{equation}
  L(\lambda, p) \defeq \underset{B}{\text{minimize}}\ \frac{1}{T}\sum_{t = 1}^T||x(t) - \sum_{\tau = 1}^pB(\tau)x(t - \tau)||_2^2 + \lambda \sum_{i, j}\big[\alpha||B_{i, j}||_2 + (1 - \alpha)||B_{i, j}||_1\big]
\end{equation}

\begin{equation}
  \underset{\lambda, p}{\text{minimize}}\ L(\lambda, p) + \mathsf{AIC}(B^{(\lambda, p)})
\end{equation}

@@

\subsection{Layered Strongly Causal Graphs}
It is clearn that Algorithm \ref{alg:pwgr} is a purely theoretical construct, and cannot be applied directly to real data.  Instead, we convert the algorithm into an heuristic and observe it's performance experimentally.  We first consider the heuristic version of Algorithm \ref{alg:pwgr} in Algorithm \ref{alg:pwgr_heuristic} and show that is a well defined procedure (note that $\ceil{x}$ denotes the integer ceiling function):

@@

  \BlankLine
  \caption{Graph Recovery Heuristic $\mathsf{pw\_scg}(F, P, \alpha)$}
  \label{alg:pwgr_heuristic}
  \Input{Estimates of pairwise Granger-causaltiy statistics $F_{ij}$ (eqn \ref{eqn:gc_statistics}), Matrix of edge probabilities $P_{ij}$ (eqn \ref{eqn:edge_inclusion_probability}), threshold $\delta$.}
  \Output{A strongly causal graph $\widehat{\gcg}$}
  \Initialize{$S = [n]$  \texttt{\# unprocessed nodes}\\
    $E = \emptyset$  \texttt{\# edges of }$\widehat{\gcg}$\\
    $k = 1$ \texttt{\# a counter used only for notation}}

  \BlankLine

  $W_\delta \leftarrow \{(i, j)\ |\ P_{ji} > 1 - \delta, F_{ji} > F_{ij}\}$  \texttt{\# candidate edges}\\
  $\mathcal{I}_0 \leftarrow \big(\sum_{j\in S: (j, i) \in W_\delta} P_{ij}, \mathsf{\ for\ }i \in S \big)$ \texttt{\# total node incident probability}\\
  $P_0 \leftarrow \{i \in S\ |\ \mathcal{I}_0(i) < \ceil{\text{min}(\mathcal{I}_0)}\}$ \texttt{\# Nodes with fewest incident edges}\\
  \If{$P_0 = \emptyset$}{
    $P_0 \leftarrow \{i \in S\ |\ \mathcal{I}_0(i) \le \ceil{\text{min}(\mathcal{I}_0)}\}$ \texttt{\# Ensure non-empty}
  }
  \BlankLine

  \While{$S \ne \emptyset$}{
    $S \leftarrow S \setminus P_{k - 1}$ \texttt{\# remove processed nodes}\\
    % $\mathcal{I}_k \leftarrow \big(\sum_{j \in S: (j, i) \in W_\delta} F_{ij}, \mathsf{\ for\ }i \in S \big)$ \texttt{\# intra-}$S$ \texttt{incident strength}\\
    $\mathcal{I}_k \leftarrow \big(\sum_{j\in S: (j, i) \in W_\delta} P_{ij}, \mathsf{\ for\ }i \in S \big)$\\
    $P_k \leftarrow \{i \in S\ |\ \mathcal{I}_k(i) < \ceil{\text{min}(\mathcal{I}_k)}\}$\\
    \If{$P_k = \emptyset$}{
      $P_k \leftarrow \{i \in S\ |\ \mathcal{I}_k(i) \le \ceil{\text{min}(\mathcal{I}_k)}\}$
    }
    \;
    \texttt{\# add strongest edges, maintaining strong causality}\\
    $U_k \leftarrow \bigcup_{r = 1}^k P_{k - r}$ \texttt{\# Include all forward edges}\\
    \For{$(i, j) \in \mathsf{sort}\Big(\{(i, j) \in U_k \times P_k\ |\ (i, j) \in W_\delta\} \mathsf{\ by\ descending\ } F_{ji}\Big)$} {
      \If{$\mathsf{is\_strongly\_causal}(E \cup \{(i, j)\})$} {
        $E \leftarrow E \cup \{(i, j)\}$
      }
    }
    $k \leftarrow k + 1$\\
  }
  \Return{$([n], E)$}
\end{algorithm}

  \BlankLine
  \caption{Filter Estimator}
  \label{alg:Bz_estimate}
  \Input{$T$ samples from a WSS process $x: \{x(t)\}_{t = 1}^T$\\
    Maximum iterations $M$\\
    Sparsity parameters $\{(\delta_m\, b_m, R_m)\}_{m = 1}^M$}
  \Output{Linear one-step-ahead estimator $\widehat{\B}(z)$}
  \Initialize{$\epsilon^{(0)}(t) = x(t)$ \texttt{\# initial error process}\\
    $m = 1$ \texttt{\# iteration counter}}
  \BlankLine
  \For{$m = 1, \ldots, M$}{
    $F \leftarrow \mathsf{pwgc}(\epsilon^{(m - 1)}(t))$ \texttt{\# estimate pairwise Granger-causality statistics}\\
    $\widehat{\gcg}_m \leftarrow \mathsf{pw\_scg}(F, \delta_m, b_m, R_m)$ \texttt{\# graph estimate (Algorithm \ref{alg:pwgr_heuristic})}\\
    $\widehat{\B}^{(m)}(z) \leftarrow \mathsf{estimate\_B}(\epsilon^{(m - 1)}(t), \widehat{\gcg}_m)$ \texttt{\# Estimate filter with topology} $\widehat{\gcg}_m$\\
    $\epsilon^{(m)}(t) \leftarrow \epsilon^{(m - 1)}(t) - \widehat{\B}^{(m)}(z)\epsilon^{(m - 1)}(t)$ \texttt{\# updated error process}\\
  }
  \BlankLine
  $\widehat{\B}(z) \leftarrow \widehat{\B}^{(M)}(z) \prod_{k = 1}^{M - 1}\big(I - \widehat{\B}^{(M - k)}(z)\big)$ \texttt{\# compute total filter}\\
  \Return{$\widehat{\B}(z)$}
\end{algorithm}

\section{Empirical Evaluation}
We have implemented simple empirical experiments in Python
\cite{scipy}, in particular we leverage the LASSO implementation from
\texttt{sklearn} \cite{sklearn} and the random graph generators from
\texttt{networkx} \cite{networkx}.  We run the same experiment on
three separate graph topologies having $n = 75$ nodes: a tree (which
is strongly causal), a random directed acyclic graph, and an Erdos
Renyi random graph with edge inclusion probability of $2 / n$.

We populate each of the edges (including self loops) with random
linear filters constructed by placing $5$ transfer function poles
uniformly at random in a disc of radius $3 / 4$ (which guarantees
stability for acyclic graphs).  The resulting system is driven by
i.i.d. Gaussian random vectors, each component having random variance
$\sigma_i^2 = 1/2 + r_i$ where $r_i \sim \text{exp}(1/2)$.  Results
are obtained for $50$ random iterations per each of $6$ dataset
lengths $T \in \{100, 500, 1000, 2500, 5000, 10000\}$.

The pairwise causality function $\mathsf{pwgc}$ of Algorithm
\ref{alg:Bz_estimate} are obtained via the residuals
$\mathbf{\epsilon}_{ij}$ of the model
$\mathbf{x}_i = \mathbf{X}_{ij}\widehat{\beta_{}} +
\mathbf{\epsilon}_{ij}$ estimated via ordinary least squares, where
$\mathbf{X}_{ij}$ includes $10$ lagged values of processes $i$ and
$j$.

The function $\mathsf{estimate_B}$ in Algorithm \ref{alg:Bz_estimate}
is carried out via the LASSO \cite{tibshirani2015statistical}, with
the regularization parameter being chosen to minimize the Bayesian
information criteria, a more conservative heuristic than the AIC.

@@

  \begin{subfigure}[b]{0.30\textwidth}
    \caption{Random Tree}
    \includegraphics[width=\linewidth]{example_tree.pdf}
  \end{subfigure}
  \begin{subfigure}[b]{0.30\textwidth}
    \caption{Random DAG}
    \includegraphics[width=\linewidth]{example_dag.pdf}
  \end{subfigure}
  \begin{subfigure}[b]{0.30\textwidth}
    \caption{Erdos-Renyi Graph}
    \includegraphics[width=\linewidth]{example_gnp.pdf}
  \end{subfigure}

  \begin{subfigure}[b]{0.30\textwidth}
    \includegraphics[width=\linewidth]{random_tree_simulation.pdf}
  \end{subfigure}
  \begin{subfigure}[b]{0.30\textwidth}
    \includegraphics[width=\linewidth]{random_dag_simulation.pdf}
  \end{subfigure}
  \begin{subfigure}[b]{0.30\textwidth}
    % \includegraphics[width=\linewidth]{random_gnp_simulation.pdf}
    \missingfigure{}
  \end{subfigure}
\end{figure}

>>>>

A second and wildly successful heuristic is the LASSO regularizer
\cite{tibshirani1996regression}, which can be understood as a natural
convex relaxation to penalizing the count of the non-zero edges.  The
LASSO enjoys strong theoretical guarantees \cite{wainwright2009sharp},
even in the case of time series data \cite{basu2015}
\cite{wong2016lasso}, variations on which have been applied elsewhere
\cite{DBLP:journals/corr/HallacPBL17} \cite{haufe2008sparse}
\cite{bolstad2011causal} \cite{he2013stationary}.

The contributions of this paper are as follows: firstly, in section
\ref{sec:theory} we study \textit{pairwise} Granger-causality
relations, providing novel theorems connecting the structure of the
causality graph to the pairwise ``causality flow'' in the system, as
well as a characterization of the sparsity pattern of matrices arising
in the Wold decomposition.  We establish sufficient conditions
(sections \ref{sec:strongly_causal_graphs},
\ref{sec:persistent_systems}) under which a fully conditional
Granger-causality graph can be recovered from pairwise tests alone
(section \ref{sec:pairwise_algorithm}).  Secondly, we propose in
section \ref{sec:structure_learning} a graph search heuristic which
implements our theoretical results to finite data samples.  Our
heuristics are compared against the LASSO algorithm in Section
\ref{sec:empirical_evaluation}.  We stress the scalability of our
algorithm which is capable of comfortably handling hundreds or
thousands of nodes on a single machine.  In section
\ref{sec:application} we develop an example application (\hl{more
  detail...}).  And provide concluding remarks on further open
problems in our conclusion (section \ref{sec:conclusion}).

% \cite{yuan2006model} as well as local search hill
% climbing (\hl{state here the results}).

@@

  \begin{enumerate}
    \item{$\mathcal{A} \perp \mathcal{B}\ |\ \mathcal{X}$}
    \item{$\linE{\beta}{\mathcal{A} \vee \mathcal{X}} = \linE{\beta}{\mathcal{X}}\ \forall \beta \in \mathcal{B}$.}
    % \item{$\linE{\beta}{\mathcal{A}} = \linE{\linE{\beta}{\mathcal{X}}}{\mathcal{A}}\ \forall \beta \in \mathcal{B}}$}
    \end{enumerate}

@@

\subsection{Model Order Selection}
\label{sec:model_order_selection}
There are a variety of methods to choose the filter orders $p_i$ and
$p_j$ \hl{TODO: cite some more}, we will focus in particular on the
Bayesian Information Criteria (BIC).  The BIC is substantially more
conservative than the Akaiake Information Criteria, and since we are
searching for \textit{sparse graphs}, we therefore prefer the BIC. For
the bivariate case we focus for simplicity on $p_i = p_j$ and write
simply\footnote{We use the same $p$ for the bivariate case, but this
  need not be the same as the corresponding univariate estimate}
$x_{ij}^{(p)}$, in which case the BIC, which we seek to
\textit{minimize} over $p$ is given by:

\begin{equation}
  \label{eqn:bic}
  \begin{aligned}
    BIC_{\text{univariate}}(p) &= T \ln \xi_i(p) + p\ln T,\\
    BIC_{\text{bivariate}}(p) &= T \ln \xi_{ij}(p) + 2p\ln T.\\
  \end{aligned}
\end{equation}

@@

% \section{Structure Learning}
% \label{sec:structure_learning}
% \subsection{Local Search Heuristics}

% \subsection{Edge-Wise Grouped LASSO}
% Minimize the sparsity promoting regularized least squares problem and choose the hyper-parameters against the Akaike information criteria.

% \begin{equation}
%   L(\lambda, p) \defeq \underset{B}{\text{minimize}}\ \frac{1}{T}\sum_{t = 1}^T||x(t) - \sum_{\tau = 1}^pB(\tau)x(t - \tau)||_2^2 + \lambda \sum_{i, j}\big[\alpha||B_{i, j}||_2 + (1 - \alpha)||B_{i, j}||_1\big]
% \end{equation}

% \begin{equation}
%   \underset{\lambda, p}{\text{minimize}}\ L(\lambda, p) + \mathsf{AIC}(B^{(\lambda, p)})
% \end{equation}

@@

% \subsection{Layered Strongly Causal Graphs}
% It is clearn that Algorithm \ref{alg:pwgr} is a purely theoretical construct, and cannot be applied directly to real data.  Instead, we convert the algorithm into an heuristic and observe it's performance experimentally.  We first consider the heuristic version of Algorithm \ref{alg:pwgr} in Algorithm \ref{alg:pwgr_heuristic} and show that is a well defined procedure (note that $\ceil{x}$ denotes the integer ceiling function):

@@

% \begin{algorithm}
%   \SetKwInOut{Input}{input}
%   \SetKwInOut{Output}{output}
%   \SetKwInOut{Initialize}{initialize}
%   \DontPrintSemicolon

%   \BlankLine
%   \caption{Graph Recovery Heuristic $\mathsf{pw\_scg}(F, P, \alpha)$}
%   \label{alg:pwgr_heuristic}
%   \Input{Estimates of pairwise Granger-causaltiy statistics $F_{ij}$ (eqn \ref{eqn:gc_statistics}), Matrix of edge probabilities $P_{ij}$ (eqn \ref{eqn:edge_inclusion_probability}), threshold $\delta$.}
%   \Output{A strongly causal graph $\widehat{\gcg}$}
%   \Initialize{$S = [n]$  \texttt{\# unprocessed nodes}\\
%     $E = \emptyset$  \texttt{\# edges of }$\widehat{\gcg}$\\
%     $k = 1$ \texttt{\# a counter used only for notation}}

%   \BlankLine

%   $W_\delta \leftarrow \{(i, j)\ |\ P_{ji} > 1 - \delta, F_{ji} > F_{ij}\}$  \texttt{\# candidate edges}\\
%   $\mathcal{I}_0 \leftarrow \big(\sum_{j\in S: (j, i) \in W_\delta} P_{ij}, \mathsf{\ for\ }i \in S \big)$ \texttt{\# total node incident probability}\\
%   $P_0 \leftarrow \{i \in S\ |\ \mathcal{I}_0(i) < \ceil{\text{min}(\mathcal{I}_0)}\}$ \texttt{\# Nodes with fewest incident edges}\\
%   \If{$P_0 = \emptyset$}{
%     $P_0 \leftarrow \{i \in S\ |\ \mathcal{I}_0(i) \le \ceil{\text{min}(\mathcal{I}_0)}\}$ \texttt{\# Ensure non-empty}
%   }
%   \BlankLine

%   \While{$S \ne \emptyset$}{
%     $S \leftarrow S \setminus P_{k - 1}$ \texttt{\# remove processed nodes}\\
%     % $\mathcal{I}_k \leftarrow \big(\sum_{j \in S: (j, i) \in W_\delta} F_{ij}, \mathsf{\ for\ }i \in S \big)$ \texttt{\# intra-}$S$ \texttt{incident strength}\\
%     $\mathcal{I}_k \leftarrow \big(\sum_{j\in S: (j, i) \in W_\delta} P_{ij}, \mathsf{\ for\ }i \in S \big)$\\
%     $P_k \leftarrow \{i \in S\ |\ \mathcal{I}_k(i) < \ceil{\text{min}(\mathcal{I}_k)}\}$\\
%     \If{$P_k = \emptyset$}{
%       $P_k \leftarrow \{i \in S\ |\ \mathcal{I}_k(i) \le \ceil{\text{min}(\mathcal{I}_k)}\}$
%     }
%     \;
%     \texttt{\# add strongest edges, maintaining strong causality}\\
%     $U_k \leftarrow \bigcup_{r = 1}^k P_{k - r}$ \texttt{\# Include all forward edges}\\
%     \For{$(i, j) \in \mathsf{sort}\Big(\{(i, j) \in U_k \times P_k\ |\ (i, j) \in W_\delta\} \mathsf{\ by\ descending\ } F_{ji}\Big)$} {
%       \If{$\mathsf{is\_strongly\_causal}(E \cup \{(i, j)\})$} {
%         $E \leftarrow E \cup \{(i, j)\}$
%       }
%     }
%     $k \leftarrow k + 1$\\
%   }
%   \Return{$([n], E)$}
% \end{algorithm}

% \begin{algorithm}
%   \SetKwInOut{Input}{input}
%   \SetKwInOut{Output}{output}
%   \SetKwInOut{Initialize}{initialize}
%   \DontPrintSemicolon

%   \BlankLine
%   \caption{Filter Estimator}
%   \label{alg:Bz_estimate}
%   \Input{$T$ samples from a WSS process $x: \{x(t)\}_{t = 1}^T$\\
%     Maximum iterations $M$\\
%     Sparsity parameters $\{(\delta_m\, b_m, R_m)\}_{m = 1}^M$}
%   \Output{Linear one-step-ahead estimator $\widehat{\B}(z)$}
%   \Initialize{$\epsilon^{(0)}(t) = x(t)$ \texttt{\# initial error process}\\
%     $m = 1$ \texttt{\# iteration counter}}
%   \BlankLine
%   \For{$m = 1, \ldots, M$}{
%     $F \leftarrow \mathsf{pwgc}(\epsilon^{(m - 1)}(t))$ \texttt{\# estimate pairwise Granger-causality statistics}\\
%     $\widehat{\gcg}_m \leftarrow \mathsf{pw\_scg}(F, \delta_m, b_m, R_m)$ \texttt{\# graph estimate (Algorithm \ref{alg:pwgr_heuristic})}\\
%     $\widehat{\B}^{(m)}(z) \leftarrow \mathsf{estimate\_B}(\epsilon^{(m - 1)}(t), \widehat{\gcg}_m)$ \texttt{\# Estimate filter with topology} $\widehat{\gcg}_m$\\
%     $\epsilon^{(m)}(t) \leftarrow \epsilon^{(m - 1)}(t) - \widehat{\B}^{(m)}(z)\epsilon^{(m - 1)}(t)$ \texttt{\# updated error process}\\
%   }
%   \BlankLine
%   $\widehat{\B}(z) \leftarrow \widehat{\B}^{(M)}(z) \prod_{k = 1}^{M - 1}\big(I - \widehat{\B}^{(M - k)}(z)\big)$ \texttt{\# compute total filter}\\
%   \Return{$\widehat{\B}(z)$}
% \end{algorithm}

\section{Empirical Evaluation}
\label{sec:empirical_evaluation}
We have implemented our empirical experiments in Python \cite{scipy},
in particular we leverage the LASSO implementation from
\texttt{sklearn} \cite{sklearn} and the random graph generators from
\texttt{networkx} \cite{networkx}.  We run the same experiment on two
separate graph topologies having $n = 50$ nodes: a strongly causal
graph and a directed acyclic graph.  These are generated respectively
by drawing a random tree and a random Erdos Renyi graph, then
directing edges from lower numbered nodes to higher numbered nodes,
the edge probabilities in the Erdos Renyi graph are tuned to result in
the same number of edges in expectation.

We populate each of the edges (including self loops) with random
linear filters constructed by placing $5$ transfer function poles
(i.e. $p = 5$) uniformly at random in a disc of radius $3 / 4$ (which
guarantees stability for acyclic graphs).  The resulting system is
driven by i.i.d. Gaussian random vectors, each component having random
variance $\sigma_i^2 = 1/2 + r_i$ where $r_i \sim \text{exp}(1/2)$.
We set $p_{\text{max}} = 15$ and collect results for $300$ trials with $T$
varying between $50$ and $5000$.

Results of our Algorithm are compared against the LASSO:

\begin{equation}
  \begin{aligned}
  \xi_{\text{LASSO}}^{(\lambda)} &= \underset{B}{\text{min}}\ \frac{1}{T}\sum_{t = p + 1}^T||x(t) - \sum_{\tau = 1}^p B(\tau) x(t - \tau)||_2^2 + \lambda \sum_{\tau = 1}^p ||\matvec B(\tau)||_1\\
  \xi_{\text{LASSO}} &= \underset{\lambda \ge 0}{\text{min}}\ \xi_{\text{LASSO}}^{(\lambda)} + \mathsf{BIC}(B_{\text{LASSO}}^{(\lambda)})\\
  \end{aligned}
\end{equation}

where $||\matvec B||_1$ emphasizes the application of a vector norm, and
$\lambda$ is the regularization parameter chosen via the BIC.

% The pairwise causality function $\mathsf{pwgc}$ of Algorithm
% \ref{alg:Bz_estimate} are obtained via the residuals
% $\mathbf{\epsilon}_{ij}$ of the model
% $\mathbf{x}_i = \mathbf{X}_{ij}\widehat{\beta_{}} +
% \mathbf{\epsilon}_{ij}$ estimated via ordinary least squares, where
% $\mathbf{X}_{ij}$ includes $10$ lagged values of processes $i$ and
% $j$.

% The function $\mathsf{estimate_B}$ in Algorithm \ref{alg:Bz_estimate}
% is carried out via the LASSO \cite{tibshirani2015statistical}, with
% the regularization parameter being chosen to minimize the Bayesian
% information criteria, a more conservative heuristic than the AIC.

@@

  \begin{subfigure}[b]{0.45\textwidth}
    \caption{Random SCG}
    \includegraphics[width=\linewidth]{example_scg.pdf}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \caption{Random DAG}
    \includegraphics[width=\linewidth]{example_dag.pdf}
  \end{subfigure}

  \begin{subfigure}[b]{0.45\textwidth}
    \includegraphics[width=\linewidth]{random_scg_simulation.pdf}
    % \missingfigure{}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \includegraphics[width=\linewidth]{random_dag_simulation.pdf}
    % \missingfigure{}
  \end{subfigure}
\end{figure}

In reference to figure \ref{fig:simulation_results} it should not be
overly surprising that our PWGC algorithm performs better than the
LASSO for the case of a strongly causal graph, since in this case the
assumptions which guarantee the correctness of Algorithm
\ref{alg:pwgr_heuristic} hold.  However, the performance is still
markedly superior in the case of a more general DAG.  Finally, we
remark that the PWGC algorithm can be extended to apply to more
general graphs via sequential application.  We will also see in
section \ref{sec:application} that our algorithm can scale effectively
to large problems.
